---
title: "Java Learning"
author: "Tao Zou"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
---

<style>
.copy-btn {
  position: absolute;
  top: 0;
  right: 0;
  background-color: #011627;
  border: none;
  border-radius: 3px;
  padding: 5px;
  cursor: pointer;
  font-family: 'Times New Roman';
}
</style>

```{r include=FALSE}
library(knitr)
library(kableExtra)

setwd("D:/Java_workspace/JavaLearning/")
```

# Data Type
## Primitive data type
```{r echo=FALSE, warning=FALSE}
mydf <- data.frame(
  column1 = c("Data Type", "Size", "Range"),
  column2 = c('byte', '1 byte', '$-128$ to $127$'),
  column3 = c('short', '2 bytes', '$-2^{16-1}$ to $2^{16-1}-1$'),
  column4 = c('int', '4 bytes', '$-2^{32-1}$ to $2^{32-1}-1$'),
  column5 = c('long', '8 bytes', '$-2^{64-1}$ to $2^{64-1}-1$'),
  column6 = c('float', '4 bytes', ''),
  column7 = c('double', '8 bytes', ''),
  column8 = c('boolean', '1 bit', ''),
  column9 = c('char', '2 bytes', '')
)
kable(t(mydf), "html", booktabs = T, col.names = NULL, row.names=F, align = "c") %>%
  kable_styling(bootstrap_options = 'bordered', latex_options = "striped", full_width = F)
```

## Array
`int[]`, `String[]`

```java
// 数组的创建
String[] stringArr = new String[size];  // 创建一个固定大小的String数组
String[] stringArr = {"abc", "ABC"};  // 创建数组的同时初始化数组中元素
int[][] intArr = {{1, 2, 3}, {4, 5, 6}};

// 数组的拷贝
String[] newStringArr = stringArr;  // 这是共享地址
String[] newStringArr = Arrays.copyOf(stringArr, stringArr.length);  // 重新创建一个新的数组实例，其中第二个参数为新数组长度。

// 数组排序
int[] intArr = {4, 1, 5, 6};
Arrays.sort(intArr);  // Arrays.sort()方法基于快速排序。

// 打印数组
System.out.println(Arrays.deepToString(intArr));  // [[1, 2, 3], [4, 5, 6]]
System.out.println(Arrays.toString(stringArr));  // [abc, ABC]
```

## String
```java
public final class String implements java.io.Serializable, Comparable<String>, CharSequence
```

- Immutability

`String` 对象一旦被创建就不能被改变，这也意味着任何`String`实例方法的调用都不会改变实例本身。

- String Pool

用相同的字面量创建`String`实例时，会直接返回池中的引用，不会创建新的对象，比如：

```java
String str1 = "Hello";
String str2 = "Hello";
System.out.println(str1 == str2);  // true

String str1 = new String("Hello");
String str2 = new String("Hello");
System.out.println(str1 == str2);  // false
```

### static methods
- `String.valueOf()`

```
// 将基本数据类型转化为字符串
double num = 3.1415;
String numStr = String.valueOf(num);
// 将char[]类型转化为字符串
char[] charArr = {'A', 'B', 'C'};
String charArrString = String.valueOf(charArr);  // ABC
```

- `String.format()`

`String.format()`用于创建格式化字符串。

```{r echo=FALSE, warning=FALSE}
mydf <- data.frame(
  column1 = c("格式说明符", "描述"),
  column2 = c('%s', '字符串'),
  column3 = c('%d', '十进制整数'),
  column4 = c('%o', '八进制整数'),
  column5 = c('%x', '十六进制整数'),
  column6 = c('%f', '浮点数'),
  column7 = c('%c', '单个字符'),
  column8 = c('%b', '布尔值'),
  column9 = c('%n', '换行符')
)
kable(t(mydf), "html", booktabs = T, col.names = NULL, row.names=F, align = "c") %>%
  kable_styling(bootstrap_options = 'bordered', latex_options = "striped", full_width = F)
```

```java
// 控制浮点数精度（四舍五入）
String.format("%.2f", 3.14559);  // 3.15
// 对齐与填充。例如：包含Hello在内一共是10个字符，右对齐
String.format("|%10s|%-10s|", "Hello", "World");  // |     Hello|World     |
// 将十进制数8转化为八进制数10
String.format("%o", 8);
// 补0
String.format("补零: %07.2f", (float) 123);  // 0123.00
```

- `String.join()`

```java
// 使用指定的分隔符连接多个String
String str = String.join(", ", "Hello", "World", "Java")
```

### instance methods
- `.length()`

Return the length of a `String`.

- `.charAt(int index)`

Return the char at the *index* position.

- `.indexOf(String str)` or `.indexOf(char myChar)`

Return the index of the `String` or `char` when it appears at the first time. Return $-1$ when `String` or `char` is illegal.

- `.substring(int beginIndex, int endIndex)`

Return a sub-string from the *beginIndex* position to the *endIndex-1* position.

- `.replace(char oldChar, char newChar)`

Return a new `String` in which all of the *oldChar* are replaced by *newChar*. 

- `.toLowerCase()`

- `.toUpperCase()`

- `.toCharArray()`

## StringBuilder
- 可变性：可追加、插入、删除、修改字符。

- 线程不安全：例如在两个线程中同时给一个`StringBuilder`追加元素会导致该`StringBuilder`增加的元素总数小于两个线程中增加元素的总和。

`StringBuilder`在单线程环境中性能较好，多线程环境中不安全。

`StringBuffer`在单线程环境中性能较差，多线程环境中安全。

```java
StringBuilder sb = new StringBuilder("Hello, World");
```

### static methods

### instance methods
- `.length()`

返回长度。

- `.append()`

追加字符串。

- `.insert(int index, String myStr)`

插入字符串。

- `.delete(int beginIndex, int endIndex)`

删除字符串，从*beginIndex*到*endIndex-1*。

- `.deleteChatAt(int index)`

删除指定位置的字符。

- `.toString()`

转化为`String`对象。


## Integer
### static methods
- `Integer.parseInt()`

```java
// 将String转化为int
Integer.parseInt("13245");
// 将String按照其本身的进制转化为十进制int类型
Integer.parseInt("1000", 2);  // 8
```

- `Integer.toString()`

Transfer `int` to `String`.

- `Integer.toBinaryString(int num)`

```java
// 将int转化为二进制字符串
Integer.toBinaryString(8);
```

### instance methods



# Java Modifiers
## Access Modifiers
For **class**,

```{r echo=FALSE, warning=FALSE}
mydf <- data.frame(
  column1 = c("Modifier", "Description"),
  column2 = c('public', 'The class is accessible by any other class'),
  column3 = c('default', 'The class is only accessible by classes in the same package.')
)
kable(t(mydf), "html", booktabs = T, col.names = NULL, row.names=F, align = "c") %>%
  kable_styling(bootstrap_options = 'bordered', latex_options = "striped", full_width = F)
```

For **attribute**, **method**, **constructor**,

```{r echo=FALSE, warning=FALSE}
mydf <- data.frame(
  column1 = c("Modifier", "Description"),
  column2 = c('public', 'The code is accessible for all classes.'),
  column3 = c('protected', 'The code is accessible in the same package. And the code is accessible in the subclass.'),
  column4 = c('default', 'The code is only accessible in the same package.'),
  column5 = c('private', 'The code is only accessible within the declared class.')
)
kable(t(mydf), "html", booktabs = T, col.names = NULL, row.names=F, align = "c") %>%
  kable_styling(bootstrap_options = 'bordered', latex_options = "striped", full_width = F)
```

## Non-Access Modifier
For **class**,

```{r echo=FALSE, warning=FALSE}
mydf <- data.frame(
  column1 = c("Modifier", "Description"),
  column2 = c('final', 'The class cannot be inherited by other classes.'),
  column3 = c('abstract', 'The class is used to be inherited. The class cannot be used to create objects.')
)
kable(t(mydf), "html", booktabs = T, col.names = NULL, row.names=F, align = "c") %>%
  kable_styling(bootstrap_options = 'bordered', latex_options = "striped", full_width = F)
```

For **attribute** and **method**,

```{r echo=FALSE, warning=FALSE}
mydf <- data.frame(
  column1 = c("Modifier", "Description"),
  column2 = c('final', 'The attribute or method cannot be modified.'),
  column3 = c('static', 'The attribute or method belongs to the class , rather than an object'),
  column4 = c('abstract', 'Only be used on methods in an abstract class.'),
  column5 = c('transient', ''),
  column6 = c('synchronized', ''),
  column7 = c('volatile', '')
)
kable(t(mydf), "html", booktabs = T, col.names = NULL, row.names=F, align = "c") %>%
  kable_styling(bootstrap_options = 'bordered', latex_options = "striped", full_width = F)
```

# interface
**interface** is a special `abstract` class. Every attribute in it is treated as `public`, `static` and `final`; Every method in it is treated as `public` and `abstract`

**Functional interface** can only contain one abstract method. For example:

```java
public interface MessageCreator {
    Message createMessage(Session session) throws JMSException;
}
```

And I can use Lambda expression to implement the abstract method in a functional interface. For example:

```java
MessageCreator messageCreator = session -> session.createObjectMessage();
```


# Common Used Class
## Arrays
**Arrays** like `String[]` or `int[]` is static array, the length of which is fixed.  

```{java eval=FALSE, include=TRUE}
import java.util.Arrays;

public class Main {
    public static void main(String[] args) {

        String[] myArray = {"item1", "item2"};
        System.out.println(myArray[0]);  // Show the first element of myArray.
        System.out.println(myArray);  // Show the hash code of the memory address of an array object.
        System.out.println(Arrays.toString(myArray));  // Show all of the items in String daya type of an Array.
        System.out.println(myArray.length);  // Show the length of a String[]. 
        
    }
}
```

```{java eval=FALSE, include=TRUE}
import java.util.Arrays;

public class Main {
    public static void main(String[] args) {

        char[] charArray = s.toCharArray();
        Arrays.sort(charArray);  // Sort an Array.
    }
}
```

## ArrayList and LinkedList
```{java eval=FALSE, include=TRUE}
import java.util.ArrayList;

public class Main {
    public static void main(String[] args) {

        ArrayList<String> myList = new ArrayList<String>();
        myList.add("A");
        myList.add("B");
        myList.add("C");
        System.out.println(myList.get(1));// "B"
        myList.remove(0);
    }
}
```

`.remove()` method can remove an ArrayList's item both by index and by value. If the items in an ArrayList are `int` data type, and I want to remove the item (for example $5$) by its value, then I should use `.remove(Integer.valueOf(5))`. If I use  `.remove(5)`, the item with index of $5$ will be removed.

**ArrayList** is based on dynamic array. **LinkedList** is based on linked structure. 

Use **ArrayList** for storing and accessing data.

Use **LinkedList** to manipulate data.

## HashMap
```{java eval=FALSE, include=TRUE}
import java.util.HashMap;

public class Main {
    public static void main(String[] args) {
        HashMap<int, String> myHashTable = new HashMap<int, String>();
        myHashTable.put(0, "item1");
        System.out.println(myHashTable.get(0));
        myHashTable.remove(0);  // remove target item.
        myHashTable.clear();  // remove all items.
        myHashTable.keySet();  // java.util.HashMap$KeySet, used for loop through keys in a HashTable.
        myHashTable.values();  // java.uitl.HashMap$Values, used for loop through values in a HashTable.
        myHashTable.containsKey(0)  // to check if a key in a HashTable.
    }
}
```

## HashSet
A HashSet is a collection of items where every item is unique.

```{java eval=FALSE, include=TRUE}
import java.util.HashSet;

public class Main {
    public static void main(String[] args) {
        HashSet<String> myHashSet = new HashSet<String>();
        myHashSet.add("item1");
        myHashSet.add("item2");
        myHashSet.contains("item3");  // check if "item3" in myHashSet.
        myHashSet.remove("item2");
        myHashSet.clear();
        myHashSet.size();
        // myHashSet1.euqals(myHashSet2)  check if two HashSets have same items.
    }
}
```

# Java Polymorphism
When instantiating a subclass, I can declare the variable type as its parent class' name. But when doing this, I cannot use attributes and methods unique to the subclass. 

```{java eval=FALSE, include=TRUE}
public class PolymorphismExample {
    public static void main(String[] args) {
        Animal myAnimal = new Animal();
        Animal myDog = new Dog();
        Animal myCat = new Cat();

        myAnimal.speak(); // Output: This animal speaks in its own way.
        myDog.speak();    // Output: Dog barks.
        myCat.speak();    // Output: Cat meows.
        
        Animal[] animals = {myAnimal, myDog, myCat};
        for (Animal animal : animals) {
            animal.speak(); // Call the speak method on each type of animal
        }
    }
}
```

# Threads
1. 利用`Runnable`创建子线程。

`Runnable`的定义如下：

```java
@FunctionalInterface
public interface Runnable {
    void run(); 
}
```

`Runnable`创建子线程。

```java
Runnable task = () -> {System.out.println("This is thread 1");};
Thread thread1 = new Thread(task, "My thread 1");
thread1.start();  // start the thread1

try {
    thread1.join();  // stop the main thread and wait for thread1 to complete 
} catch (InterruptedException e) {
    e.printStackTrace();
}  // 要使用try-catch结构或在其所在的方法添加throws InterruptedException
```

2. 利用`Thread`创建子线程

```java
public class MyThread extends Thread {
    public void run() {
        System.out.println("This is my thread");
    }
}
```

### 两种创建线程的方法的示例

```java
public class Main extends Thread {
    public static void main(String[] args) throws InterruptedException {
        Runnable task = () -> {System.out.println("This is thread 1");};  // 这是thread1的run方法
        Thread thread1 = new Thread(task, "My thread 1");
        Main thread2 = new Main();
        thread2.start();
        thread1.start();
        for (int i=0; i<10; i++) {
            System.out.println("Outside");
            Thread.sleep(10);
        }
    }

    // 这是thread2的run方法
    public void run() {
        for (int i=0; i<10; i++) {
            System.out.println("Inside");
            try {
                Thread.sleep(100);
            } catch (InterruptedException e) {
                e.printStackTrace();
            }
        }
    }
}
```


















