---
title: "Java Learning"
author: "Tao Zou"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
---

<style>
.copy-btn {
  position: absolute;
  top: 0;
  right: 0;
  background-color: #011627;
  border: none;
  border-radius: 3px;
  padding: 5px;
  cursor: pointer;
  font-family: 'Times New Roman';
}
</style>

<script>
document.addEventListener('DOMContentLoaded', (event) => {
  // 创建复制到剪贴板的函数
  function copyToClipboard(str) {
    const el = document.createElement('textarea');
    el.value = str;
    document.body.appendChild(el);
    el.select();
    document.execCommand('copy');
    document.body.removeChild(el);
  };

  // 为每个代码块添加复制按钮
  document.querySelectorAll('pre code').forEach((block) => {
    const btn = document.createElement('button');
    btn.className = 'copy-btn';
    btn.textContent = 'Copy';
    btn.addEventListener('click', () => {
      // 复制文本到剪贴板
      copyToClipboard(block.textContent);
      // 更新按钮文本为 "Copied"
      btn.textContent = 'Copied';
      // 设置两秒后恢复按钮文本
      setTimeout(() => {
        btn.textContent = 'Copy';
      }, 2000); // 2000 毫秒后执行
    });
    block.parentNode.appendChild(btn);
  });
});
</script>

```{r include=FALSE}
library(knitr)
library(kableExtra)

setwd("D:/Java_workspace/JavaLearning/")
```

# Data Type
## String
```java
public final class String implements java.io.Serializable, Comparable<String>, CharSequence
```

- Immutability

`String` 对象一旦被创建就不能被改变，这也意味着任何`String`实例方法的调用都不会改变实例本身。

- String Pool

用相同的字面量创建`String`实例时，会直接返回池中的引用，不会创建新的对象，比如：

```java
String str1 = "Hello";
String str2 = "Hello";
System.out.println(str1 == str2);  // true

String str1 = new String("Hello");
String str2 = new String("Hello");
System.out.println(str1 == str2);  //false
```

### Instance methods



### Static methods
- `String.valueOf()`

```
// 将基本数据类型转化为字符串
double num = 3.1415;
String numStr = String.valueOf(num);
```

- `String.format()`

```{r echo=FALSE, warning=FALSE}
mydf <- data.frame(
  column1 = c("格式说明符", "描述"),
  column2 = c('%s', '字符串'),
  column3 = c('%d', '十进制整数'),
  column4 = c('%o', '八进制整数'),
  column5 = c('%x', '十六进制整数'),
  column6 = c('%f', '浮点数'),
  column7 = c('%c', '单个字符'),
  column8 = c('%b', '布尔值'),
  column9 = c('%n', '换行符')
)
kable(t(mydf), "html", booktabs = T, col.names = NULL, row.names=F, align = "c") %>%
  kable_styling(bootstrap_options = 'bordered', latex_options = "striped", full_width = F)
```

```java
// 控制浮点数精度（四舍五入）
String.format("%.2f", 3.14559);  // 3.15
// 对齐与填充。例如：包含Hello在内一共是10个字符，右对齐
String.format("|%10s|%-10s|", "Hello", "World");  // 
```

- `String.join()`

```java
// 使用指定的分隔符连接多个String
String str = String.join(", ", "Hello", "World", "Java")
```






**String**

```{java eval=FALSE, include=TRUE}
import java.util.Arrays;

public class Main {
    public static void main(String[] args) {

        String myString = "abcdefg";
        System.out.println(myString.length());  // Show a the length of String data type.
        char[] myChars = myString.toCharArray();  // Convert a String into a char array.
        // String.valueOf(myChars) can convert char[] Array into a String.
    }
}
```

## Integer
### Static methods
`Integer.parseInt()`

```java
\\ 将字符串按照其本身的进制转化为int类型
Integer.parseInt("1000", 2); \\ 8
```

`Integer.toBinaryString()`


# Java Modifiers
## Access Modifiers
For **class**,

```{r echo=FALSE, warning=FALSE}
mydf <- data.frame(
  column1 = c("Modifier", "Description"),
  column2 = c('public', 'The class is accessible by any other class'),
  column3 = c('default', 'The class is only accessible by classes in the same package.')
)
kable(t(mydf), "html", booktabs = T, col.names = NULL, row.names=F, align = "c") %>%
  kable_styling(bootstrap_options = 'bordered', latex_options = "striped", full_width = F)
```

For **attribute**, **method**, **constructor**,

```{r echo=FALSE, warning=FALSE}
mydf <- data.frame(
  column1 = c("Modifier", "Description"),
  column2 = c('public', 'The code is accessible for all classes.'),
  column3 = c('protected', 'The code is accessible in the same package. And the code is accessible in the subclass.'),
  column4 = c('default', 'The code is only accessible in the same package.'),
  column5 = c('private', 'The code is only accessible within the declared class.')
)
kable(t(mydf), "html", booktabs = T, col.names = NULL, row.names=F, align = "c") %>%
  kable_styling(bootstrap_options = 'bordered', latex_options = "striped", full_width = F)
```

## Non-Access Modifier
For **class**,

```{r echo=FALSE, warning=FALSE}
mydf <- data.frame(
  column1 = c("Modifier", "Description"),
  column2 = c('final', 'The class cannot be inherited by other classes.'),
  column3 = c('abstract', 'The class is used to be inherited. The class cannot be used to create objects.')
)
kable(t(mydf), "html", booktabs = T, col.names = NULL, row.names=F, align = "c") %>%
  kable_styling(bootstrap_options = 'bordered', latex_options = "striped", full_width = F)
```

For **attribute** and **method**,

```{r echo=FALSE, warning=FALSE}
mydf <- data.frame(
  column1 = c("Modifier", "Description"),
  column2 = c('final', 'The attribute or method cannot be modified.'),
  column3 = c('static', 'The attribute or method belongs to the class , rather than an object'),
  column4 = c('abstract', 'Only be used on methods in an abstract class.'),
  column5 = c('transient', ''),
  column6 = c('synchronized', ''),
  column7 = c('volatile', '')
)
kable(t(mydf), "html", booktabs = T, col.names = NULL, row.names=F, align = "c") %>%
  kable_styling(bootstrap_options = 'bordered', latex_options = "striped", full_width = F)
```

# interface
**interface** is a special `abstract` class. Every attribute in it is treated as `public`, `static` and `final`; Every method in it is treated as `public` and `abstract`

**Functional interface** can only contain one abstract method. For example:

```java
public interface MessageCreator {
    Message createMessage(Session session) throws JMSException;
}
```

And I can use Lambda expression to implement the abstract method in a functional interface. For example:

```java
MessageCreator messageCreator = session -> session.createObjectMessage();
```


# Common Used Class
## Arrays
**Arrays** like `String[]` or `int[]` is static array, the length of which is fixed.  

```{java eval=FALSE, include=TRUE}
import java.util.Arrays;

public class Main {
    public static void main(String[] args) {

        String[] myArray = {"item1", "item2"};
        System.out.println(myArray[0]);  // Show the first element of myArray.
        System.out.println(myArray);  // Show the hash code of the memory address of an array object.
        System.out.println(Arrays.toString(myArray));  // Show all of the items in String daya type of an Array.
        System.out.println(myArray.length);  // Show the length of a String[]. 
        
    }
}
```

```{java eval=FALSE, include=TRUE}
import java.util.Arrays;

public class Main {
    public static void main(String[] args) {

        char[] charArray = s.toCharArray();
        Arrays.sort(charArray);  // Sort an Array.
    }
}
```

## ArrayList and LinkedList
```{java eval=FALSE, include=TRUE}
import java.util.ArrayList;

public class Main {
    public static void main(String[] args) {

        ArrayList<String> myList = new ArrayList<String>();
        myList.add("A");
        myList.add("B");
        myList.add("C");
        System.out.println(myList.get(1));// "B"
        myList.remove(0);
    }
}
```

`.remove()` method can remove an ArrayList's item both by index and by value. If the items in an ArrayList are `int` data type, and I want to remove the item (for example $5$) by its value, then I should use `.remove(Integer.valueOf(5))`. If I use  `.remove(5)`, the item with index of $5$ will be removed.

**ArrayList** is based on dynamic array. **LinkedList** is based on linked structure. 

Use **ArrayList** for storing and accessing data.

Use **LinkedList** to manipulate data.

## HashMap
```{java eval=FALSE, include=TRUE}
import java.util.HashMap;

public class Main {
    public static void main(String[] args) {
        HashMap<int, String> myHashTable = new HashMap<int, String>();
        myHashTable.put(0, "item1");
        System.out.println(myHashTable.get(0));
        myHashTable.remove(0);  // remove target item.
        myHashTable.clear();  // remove all items.
        myHashTable.keySet();  // java.util.HashMap$KeySet, used for loop through keys in a HashTable.
        myHashTable.values();  // java.uitl.HashMap$Values, used for loop through values in a HashTable.
        myHashTable.containsKey(0)  // to check if a key in a HashTable.
    }
}
```

## HashSet
A HashSet is a collection of items where every item is unique.

```{java eval=FALSE, include=TRUE}
import java.util.HashSet;

public class Main {
    public static void main(String[] args) {
        HashSet<String> myHashSet = new HashSet<String>();
        myHashSet.add("item1");
        myHashSet.add("item2");
        myHashSet.contains("item3");  // check if "item3" in myHashSet.
        myHashSet.remove("item2");
        myHashSet.clear();
        myHashSet.size();
        // myHashSet1.euqals(myHashSet2)  check if two HashSets have same items.
    }
}
```

# Java Polymorphism
When instantiating a subclass, I can declare the variable type as its parent class' name. But when doing this, I cannot use attributes and methods unique to the subclass. 

```{java eval=FALSE, include=TRUE}
public class PolymorphismExample {
    public static void main(String[] args) {
        Animal myAnimal = new Animal();
        Animal myDog = new Dog();
        Animal myCat = new Cat();

        myAnimal.speak(); // Output: This animal speaks in its own way.
        myDog.speak();    // Output: Dog barks.
        myCat.speak();    // Output: Cat meows.
        
        Animal[] animals = {myAnimal, myDog, myCat};
        for (Animal animal : animals) {
            animal.speak(); // Call the speak method on each type of animal
        }
    }
}
```





